%-------------------------
% Resume in Latex
% Author : Benjamin Giles
% License : MIT
%------------------------

\documentclass[11pt]{article}

\input{glyphtounicode}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Benjamin Giles} & Email : \href{mailto:btgiles@gmail.com}{btgiles@gmail.com} \\
  \href{https://github.com/benkant}{https://github.com/benkant} & Mobile : +61-400-732-837 \\
  \href{https://www.linkedin.com/in/rbp-0xdeadbeef/}{https://www.linkedin.com/in/rbp-0xdeadbeef/}
\end{tabular*}

%
%--------PROGRAMMING SKILLS------------
\section{Abilities}
  \resumeSubHeadingListStart
    \resumeSubItem{Recently used languages}{Python, C, SQL, Java, MATLAB, Bash.}
    \resumeSubItem{Technical skills}{version control, machine learning, operating system internals, low level systems and network programing, geographic information systems, applied mathematics, statistics, mentoring and instruction, CI/CD.}
    \resumeSubItem{Technologies}
      {AWS/GCP: (datastores, load balancers, orchestration, security profiles, compute, analytics), RDBMS, OpenGL, scientific Python, UNIX (various), Wireshark, ArcGIS Desktop/Server, LLVM, IDA Pro, x64dbg.}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Recent Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Australian Defence Force Academy}{Canberra, Australia}
      {Cyber Security (Advanced Tradecraft)}{Feb 2020 - July 2020}
        \resumeItemListStart
          \resumeItem{Post-graduate Coursework}
            {Australian Signals Directorate information security best practices, reverse engineering, electronic warfare tactics, techniques, and procedures, radio frequency device assessment and exploitation, digital forensics, exploit development, domestic computer/network/electromagnetic spectrum legalities, cryptography, foreign actor engagement issues, secure code review, machine learning for malware detection}
          \resumeItemListEnd

    \resumeSubheading
      {FEISAR Pte Ltd}{Singapore}
      {Senior Analysis Programmer}{June 2014 - December 2019}
      \resumeItemListStart
          {Delivered software consulting and development services to oil \& gas and fintech sectors.}
            \resumeItem{Pin Payments}
              {Developed a machine learning model in MATLAB to predict customer risk during onboarding to reduce fraud loss.}

            \resumeItem{Player, with GIS-Pax Pty Ltd}
              {Implemented features in the de facto standard prospect evaluation tool for geoscientists used by all oil and gas supermajors (ExxonMobil, BP, Royal Dutch Shell, Chevron, Total, Conoco Phillips) and the majority of mid-sized firms (Hess, Repsol, Petronas, Equinor, Petrobras). Written with ESRI SDK's for Windows Workstations.}

            \resumeItem{Player QwikVol, with GIS-Pax Pty Ltd}
              {Designed, implemented and formally tested for stability several numerical algorithms, including a Markov Chain Monte Carlo simulation to produce probability distributions of expected oil, gas and condensate in prospects. The result of this is the primary information for a \$100m exploration drilling decision. Designed for portability, it runs on x64 workstations and Apple A-Series ARM CPU's. Technologies used: C, MATLAB, C\#, Mathematica, Math.NET Numerics, a whiteboard and lots of pens.}

            \resumeItem{PlayHouse, with GIS-Pax Pty Ltd}
              {Lead engineering on a team that developed a geospatial data pipeline that consumed data produced by geoscientists to feed visualisation and decision support systems. These were consumed by oil \& gas exploration economists and senior exploration management. Implemented in Python, C, C\#, shells scripts, PowerShell, and integrated with ArcGIS Server.}

            \resumeItem{Consulting, with GIS-Pax Pty Ltd}
              {Conducted technical pre-sales and onsite deployments worldwide, and in the cloud (GCP, Azure and AWS).}

            \resumeItem{Professional development in Mathematics and Machine Learning}
              {Multivariable Calculus, Linear Algebra, Differential Equations, Vector Calculus, Numerical Methods, Number Theory, Probability, Statistics, Supervised Learning, Unsupervised Learning}
      \resumeItemListEnd

    \resumeSubheading
      {Pin Payments}{Melbourne, Australia}
      {Engineer Manager}{May 2012 - May 2014}
      \resumeItemListStart
        \resumeItem{Core Payment Systems}
          {Lead software design, architecture, development and infrastructure for international payments, foreign exchange, fraud detection and credit card processing.}
        \resumeItem{Financial system integrations}
          {Managed relationships and technical requirements with upstream financial providers.}
        \resumeItem{Leadership}
          {Hired and managed five technical staff, and several contractors, defining software development processes and best practices.}
        \resumeItem{Acqusition prospect analysis}
          {Performed technical and economic due diligence of acquisitions.}
        \resumeItem{Dev/test/prod/analysis environment}
          {Owned DevSecOps automation in AWS, including HA production and high security internal analytics systems}
        \resumeItem{Data ETL for analytics}
          {Setup, schema design and management of Amazon Redshift for use by Tableau users in operations and management.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Further Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {ActiveEight}{Australia}
        {Freelance Programmer}{Feb 2003 - May 2012}
        \resumeItemListStart
          \resumeItem{Department of Defence, Nova Systems}
            {Geospatial data analysis tools, written in C, C++, Python, Java}
          \resumeItem{iiNet}
            {IP telecommunications management systems, written in Perl and DB/2 on Debian}
          \resumeItem{Spoon Media}
            {Statistical analysis tools for a reproductive medicine startup, written in Perl}
        \resumeItemListEnd

    \resumeSubheading
      {ESRI Australia}{Canberra, Australia}
      {Geographic Information Systems Programmer}{May 2000 - Jan 2003}
        \resumeItemListStart
          \resumeItem{Consulting at Department of Defence}
            {Developed spatial data transformation pipeline}
          \resumeItem{ActewAGL}
            {Developed tool to translate Autodesk CAD models into a spatial database}
          \resumeItem{Software Development}
            {Designed, developed, and tested workstation \& server-based GIS products for using Sun, SGI, DEC, Microsoft, and GNU C/C++ compilers with ESRI's SDK's}
          \resumeItem{Geospatial analysis}
            {Performed ad hoc geospatial data analysis in Perl}
          \resumeItem{Consulting}
            {Provided technical support for federal government ArcGIS programmers and analysts using ESRI and Microsoft SDKs}
          \resumeItem{Training Delivery}
            {Delivered ESRI certification track training courses}
        \resumeItemListEnd

    \resumeSubheading
      {Eclipse Group / Delloite Digital}{Melbourne, Australia}
      {System Programmer}{Dec 1997 - Apr 2000}
        \resumeItemListStart
        \resumeItem{Deloitte Touche Tohmatsu stake in Eclipse Group Pty Ltd}
          {Oversaw hiring of 20 technical staff and provisioning of Linux servers, Cisco network infrastructure, and Mac workstations for the expansion to Melbourne. This team ultimately became what is known today as Deloitte Digital.}
        \resumeItem{Multimedia software development}
          {Designed, developed, and tested desktop real-time 2D/3D multimedia software and libraries for macOS and Windows in Java, C++, and OpenGL.}
        \resumeItem{Server-side development}
          {Apache CGI script development on Linux servers using Perl, C, and shell scripts}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

    %-----------PROJECTS-----------------
\section{Other noteworthy projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Royal Australian Navy}
      {Large volume data processing system deployed on vessels using NetCDF data from other Defence agencies. Pipeline written in Java- embedded system written in Qt/C++}
    \resumeSubItem{OpenAI}
      {Contribution of MATLAB client for OpenAI's gym used to measure the performance of deep reinforcement learning agents.}
    \resumeSubItem{RMIT \& Defence Science Organisation}
      {Researched mobile ad hoc network protocol performance using simulations sampling from large multi-nation wargame datasets.}
    \resumeSubItem{Victorian Government}
      {Developed fire models and visualisation used by emergency personel and operations staff.}
    \resumeSubItem{Diploma of Screenwriting - Film and Television Institute}
      {Wrote a number of spec scripts, and directed music videos including writing custom VFX software \href{https://github.com/benkant/FXPlug-cloner}{https://github.com/benkant/FXPlug-cloner}.}
    \resumeSubItem{Spoon Media}
      {Developed a WYSIWYG website builder written entirely in the browser. Backend development in Drupal, front-end in JavaScript.}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Australian Defence Force Academy @ UNSW Canberra}{Canberra, Australia}
      {Master of Cyber Security (Advanced Tradecraft)}{Feb. 2020 -- Dec. 2021 (Expected)}
    \resumeSubheading
      {Royal Melbourne Institute of Technology}{Melbourne, Australia}
      {Master of Computing in Distributed Systems (Awarded with Distinction);  GPA: 3.9/4}{Mar. 2011 -- Dec. 2014}
    \resumeSubheading
      {Australian National University}{Canberra, Australia}
      {Bachelor of Science/Bachelor of Arts (Mathematics and Philosophy) - Incomplete}{Mar. 2000 -- Dec. 2002}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
